### 2008-08-17 doc/ws-quick-guide/ws-quick-guide.tex
Easy read - but it does not give instructions on what to do after a "make install" of the ARC-1 sources (or after the installation of any binary package). There was some recent update on the grid monitor, right? This would be nice to be mentioned, so people would know better how to trace their jobs.

The Advanced Resource Connector (ARC) middleware~\cite{arc}, introduced by
NorduGrid~\cite{nordugrid}, is an open source software solution
enabling production quality computational and data grids.

Since the first release (May 2002) the middleware has been deployed and
been used in production environments. Emphasis is put on scalability,
stability, reliability and performance of the middleware. A growing
number of grid projects, like NDGF~\cite{ndgf}, Swegrid~\cite{swegrid} or Swiss
National Grid Association~\cite{swing} has chosen ARC as their middleware.

This document provides a quick usage guide to the new Web Service (WS)
components of ARC, often referred to as ARC1 components. WS design of ARC is
based on a service container -- the \textit{Hosting Environment Daemon (HED)},
and different grid capabilities are implemented as Web Services residing in HED.

Currently included components are:
\begin{itemize}
\item an OGSA BES~\cite{ogsa-bes} compliant execution service --
\textit{ARC Resource-coupled EXecution service (A-REX)}~\cite{arex}
\item an \textit{Echo} service (for testing purposes)
\end{itemize}

@@

The core part of middleware is written in C/C++. Building the software
from source or installing a precompiled binary requires different external
packages, furthermore the client and server packages have different dependencies
too. Below a list of the explicit requirements is shown:

@@

@@

Please note that you can run similar \texttt{apinfo} request against any ARC1
service except Echo service. Output should always be XML description of service.

@@

Many information about functionality and configuration of various components
may be found inside corresponding configuratrion XML schemas.

@@

The open source development of the ARC middleware is coordinated by the
NorduGrid Collaboration. Currently, the main contributor is the KnowARC
project~\cite{knowarc}, but the Collaboration is open to new members.
Contributions from the community to the software and the documentation is
welcomed. Sources can be downloaded from the software repository at:

@@

For a more detailed description, write access to the code repository and
further questions, write to the \texttt{nordugrid-discuss} mailing list (see
NorduGrid Web site~\cite{nordugrid} for details). Ongoing and completed Grid
Research projects and student assignments related to the middleware are listed
on the NorduGrid Web site as well.

@@

Research papers, overview talks, reference manuals, user guides,
installation instructions, conference presentations, FAQ and even
tutorial materials can be fetched from the documentation section of the
NorduGrid Web site.

Contact information is kept updated on the NorduGrid Web site.

>>>>

The Advanced Resource Connector (ARC) middleware~\cite{arc}, introduced by
NorduGrid~\cite{nordugrid}, is an open source software solution
enabling production quality computational and data grids.
Since the first release (May 2002) the middleware has been deployed and
been used in production environments. Emphasis is put on scalability,
stability, reliability and performance of the middleware. A growing
number of grid projects, like NDGF~\cite{ndgf}, Swegrid~\cite{swegrid} or Swiss
National Grid Association~\cite{swing} have chosen ARC as their middleware.

This document provides a quick usage guide to the new Web Service (WS)
components of ARC, often referred to as ARC1 components. WS design of ARC is
based on a service container -- the \textit{Hosting Environment Daemon (HED)},
and various capabilities of the grid are implemented as distinct Web Services
that reside in HED.

At the time of writing, this comprises the following components:
\begin{itemize}
\item an OGSA BES~\cite{ogsa-bes} compliant execution service --
\textit{ARC Resource-coupled EXecution service (A-REX)}~\cite{arex}
\item an \textit{Echo} service (for testing purposes)
\end{itemize}

@@

The core part of middleware is written in C/C++. To build the software
from source or installing a precompiled binary requires the prior installation
of multiple external packages. Client and server packages differ in their
dependencies to some degree. The following lists the explicit requirements:

@@

The developers of ARC have prepared packages for several Linux
distributions\footnote{The nightly build system current comprises Debian,
Ubuntu, Fedora, RedHat and OpenSuSE}. As a user of any such operating
system, the external packages are all readily available.

@@

Please note that you can run similar \texttt{apinfo} request against any ARC1
service except Echo service. Output should always be XML description of the service.

@@

Many information about functionality and configuration of various components
may be found inside the corresponding configuration XML schemas.

@@

The open source development of the ARC middleware is coordinated by the
NorduGrid collaboration. Currently, the main contributor is the KnowARC
project~\cite{knowarc}, but the Collaboration is open to new members.
Contributions from the community to the software and the documentation is
welcomed. Sources can be downloaded from the software repository at:

@@

For a more detailed description, write access to the code repository and
further questions, write to the \texttt{nordugrid-discuss} mailing list (see
NorduGrid website~\cite{nordugrid} for details). Ongoing and completed Grid
research projects and student assignments related to the middleware are listed
on the NorduGrid website as well.

@@

Research papers, overview talks, reference manuals, user guides,
installation instructions, conference presentations, FAQ and even
tutorial materials can be fetched from the documentation section of the
NorduGrid website.

Contact information is kept updated on the NorduGrid website.
